### 2014-09-21 verteidigung/bilder/tikz/SOrient.tex
...

          % Points
          \fill[opacity=1](V0) node[below left] {\( \sigma^0 \)};
		  \fill[opacity=1, red](V0) node[above left] {\( c(\sigma^0) \)} circle (1.5pt);
		  \fill[opacity=0] (V0)  circle (1.5pt);
          \fill[opacity=1] (V1)  circle (1.5pt);
          \fill[opacity=1](V2)   circle (1.5pt);
          \fill[opacity=0] (C02)  circle (1.5pt);
          \fill[opacity=1] (C01) node[below] {\( \sigma^1 \)};
		  \fill[opacity=1, red] (C01) node[above] {\( c(\sigma^1) \)} circle (1.5pt);
          \fill[opacity=0](C12)  circle (1.5pt);
          \fill[opacity=1](C) node[below] {\( \sigma^2\)};
		  \fill[opacity=1, red](C) node[above] {\( c(\sigma^2)\)} circle (1.5pt);

		 \coordinate (CC2) at (1,0.58);
          \draw[opacity=0, color=red, ->] (CC2) + (135:0.2) arc (135:405:0.2) --++ (-3pt,3pt);

		\draw[opacity=0, color=red, ->] (V0) -- (V1);

		\coordinate (CC0) at (1,1.25);
          \draw[opacity=0, color=red, ->] (V0) + (135:0.1) arc (135:405:0.1) --++ (-2pt,2pt);
\end{tikzpicture}

>>>>

          % Points
          \fill[opacity=1](V0) node[below left] {\( \sigma^0 \)} circle (1.5pt);
		  \fill[opacity=0](V0) node[above left] {\( c(\sigma^0) \)} circle (1.5pt);
		  \fill[opacity=1] (V0)  circle (1.5pt);
          \fill[opacity=1] (V1)  circle (1.5pt);
          \fill[opacity=1](V2)   circle (1.5pt);
          \fill[opacity=0] (C02)  circle (1.5pt);
          \fill[opacity=1] (C01) node[below] {\( \sigma^1 \)};
		  \fill[opacity=0] (C01) node[above] {\( c(\sigma^1) \)} circle (1.5pt);
          \fill[opacity=0](C12)  circle (1.5pt);
          \fill[opacity=1](C) node[below] {\( \sigma^2\)};
		  \fill[opacity=0](C) node[above] {\( c(\sigma^2)\)} circle (1.5pt);

		 \coordinate (CC2) at (1,0.58);
          \draw[opacity=1, color=red, ->] (CC2) + (135:0.2) arc (135:405:0.2) --++ (-3pt,3pt);

		\draw[opacity=1, color=red, ->] (V0) -- (V1);

		\coordinate (CC0) at (1,1.25);
          \draw[opacity=1, color=red, ->] (V0) + (135:0.1) arc (135:405:0.1) --++ (-2pt,2pt);
\end{tikzpicture}
